### 2019-02-27 sections/example.tex
move comment on symbols up in example

Now we develop our workflow in a top down way.
A flight booking starts with an interactive task \TS{enter (List Passenger)}
where users can enter a list of passengers.
A passenger is valid if the name is not empty and the age is at least 0.
A list of passengers is valid if each passenger is valid, and at least one of the passengers is an adult.
When the user has entered a valid list of passengers, the step after \TS{>>?} becomes enabled,
and the user can proceed to picking seats.
The task $\Enter$ is an empty editor that asks for a value of the given type.
\begin{TASK}
  let valid = \p. not (fst p == "") /\ snd p >= 0 in
  let adult = \p. snd p >= 18 in
  let allValid = \ps. all valid ps /\ any adult ps in
  let bookFlight = enter (List Passenger) >>? \ps.
    if allValid ps then chooseSeats ps else fail
\end{TASK}
A selection of seats is correct if every entered seat is free.
\begin{TASK}
  let correct = \ss. intersect ss !freeSeats == ss in
  let chooseSeats = \ps. enter (List Seat) >>? \ss.
    if correct ss /\ length ps == length ss then confirmBooking ps ss else fail
\end{TASK}

>>>>

Now we develop our workflow in a top down way.
Our flight booking starts with an interactive task \TS{enter (List Passenger)}.
A task $\Enter \tau$ is an empty editor that asks for a value of the given type $\tau$.
where users can enter a list of passengers.
A passenger is valid if the name is not empty and the age is at least 0.
A list of passengers is valid if each passenger is valid, and at least one of the passengers is an adult.
When the user has entered a valid list of passengers, the step after \TS{>>?} becomes enabled,
and the user can proceed to picking seats.
\begin{TASK}
  let valid = \p. not (fst p == "") /\ snd p >= 0 in
  let adult = \p. snd p >= 18 in
  let allValid = \ps. all valid ps /\ any adult ps in
  let bookFlight = enter (List Passenger) >>? \ps.
    if allValid ps then chooseSeats ps else fail
\end{TASK}
A selection of seats is correct if every entered seat is free.
\begin{TASK}
  let correct = \ss. intersect ss !freeSeats == ss in
  let chooseSeats = \ps. enter (List Seat) >>? \ss.
    if correct ss /\ length ps == length ss then confirmBooking ps ss else fail
\end{TASK}
